AIR4Children: Artificial Intelligence and Robotics for Children

### 2021-03-03 article/tex/main.tex
#7 correct spell errors

In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programing languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.

@@

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activitities and fig \ref{fig:tm}(c) a block diagram as a child-centre programing language.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her contributions and input as Montessori teacher. 
To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
To Leticia Vazques for her inputs as a teacher of teenagers. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To Dago Cruz for his contributions on open source AI and Robotics.
To all of you of whom with the limited time were able to contribute to this work to make a bit more solid.
Thanks to Miguel Xochicale to orchestrate AIR4Children.
\end{acks}

>>>>

In a first phase, AIR4Children project will be piloting teaching materials with our open source robots and Otto, a well known open source educational robot \cite{OttoDIY:2016}.  
Then in a second phase, and with feedback of the pilots, teaching materials with child-centre programming languages as well as the customisation of open source robots will be improved to polish a more child-centred curriculum of AIR. 
On a third phase, children and adolescents in a range of age between 6 to 14 years old will be invited to enroll on workshops to be free of charge to all the participants. 
In this regard, this initial phases of the project will help us to provide evidence of the impact of AIR in a children of different backgrounds and evaluate children's perception on the fields of AI and Robotics.

@@

That said, figure \ref{fig:tm}(a) illustrates the spiral learning technique adopted for AIR4Children to reinforce the above Montessori skills \cite{tarik2017}, fig \ref{fig:tm}(b) shows material of otto robot to develop creative exploration and engage in collaborative activities and fig \ref{fig:tm}(c) a block diagram as a child-centre programming language.

@@

%% The acknowledgments section is defined using the "acks" environment
%% (and NOT an unnumbered section). This ensures the proper
%% identification of the section in the article metadata, and the
%% consistent spelling of the heading.
\begin{acks}
To Rocio Montenegro for her contributions and input as Montessori teacher. 
To Elva Corona for her contributions on giving vision to the goals of the project. 
To Marta P\'erez, Donato Badillo-Per\'ez and Antonio Badillo-Per\'e\ for their interest as initial testers of the project. 
To Leticia V\'azquez for her inputs as a teacher of teenagers. 
To Angel Mandujano for his help on the preparation of the software frameworks for the project. 
To Dago Cruz for his contributions on open source AI and Robotics.
To all of you of whom with the limited time were able to contribute to this work to make a bit more solid.
Thanks to Miguel Xochicale to orchestrate AIR4Children.
\end{acks}
